%% Sometimes when a section can't be nicely modelled with the \entry[]... mechanism; hack our own`
\makerubrichead{\songti 研究成果}

\makesubrubrichead{\songti 期刊论文 (已发表或已接收)}

\setcounter{enum}{1}
\begin{enumerate}
  \item[\circenum] {\bfseries J.M. Duan} and H.Z. Tang, High-order accurate entropy stable finite difference schemes for
  the shallow water magnetohydrodynamics, {\em\bfseries J. Comput. Phys.}, 431: 110136, 2021.
  \item[\circenum] {\bfseries J.M. Duan} and H.Z. Tang, Entropy stable adaptive moving mesh schemes for 2D and 3D relativistic hydrodynamics,
                   {\em\bfseries J. Comput. Phys.}, 426: 109949, 2020.
  \item[\circenum] {\bfseries J.M. Duan} and H.Z. Tang, High-order accurate entropy stable nodal
                   discontinuous Galerkin schemes for the ideal special relativistic
                   magnetohydrodynamics, {\em\bfseries J. Comput. Phys.}, 421: 109731, 2020.
  \item[\circenum] {\bfseries J.M. Duan} and H.Z. Tang, High-order accurate entropy stable finite difference
                   schemes for one- and two-dimensional special relativistic hydrodynamics, {\em\bfseries Adv.
                   Appl. Math. Mech.}, 12(1): 1-29, 2020.
  \item[\circenum] {\bfseries J.M. Duan} and H.Z. Tang, An efficient ADER discontinuous Galerkin scheme for
                   directly solving Hamilton-Jacobi equation, {\em\bfseries J. Comput. Math.}, 38(1): 58-83, 2020.
  \item[\circenum] D. Ling, {\bfseries J.M. Duan} and H.Z. Tang, Physical-constraints-preserving Lagrangian
                   finite volume schemes for one- and two-dimensional special relativistic
                    hydrodynamics, {\em\bfseries J. Comput. Phys.}, 396: 507-543, 2019.
  \item[\circenum] {\bfseries 段俊明}和汤华中, 二维群集Vicsek模型的动理学方程的一个二阶精度格式,
                   {\em\bfseries 湘潭大学学报自然科学版}, 41(1): 1-14, 2019.
  \item[\circenum] {\bfseries J.M. Duan}, Y.Y. Kuang, and H.Z. Tang, Model reduction of a kinetic swarming
                    model by operator projection, {\em\bfseries East Asian J. Appl. Math.}, 8(1): 151-180, 2018.
\end{enumerate}

\makesubrubrichead{\songti 预印本}
\begin{enumerate}
  \item[\circenum] {\bfseries J.M. Duan} and H.Z. Tang, An analytical solution of the isentropic vortex problem in the special relativistic magnetohydrodynamics,
  submitted to {\em\bfseries J. Comput. Phys.},
  \href{https://arxiv.org/abs/2107.01966}{arXiv: 2107.01966}, Jul 5, 2021.
  \item[\circenum] {\bfseries J.M. Duan} and H.Z. Tang, High-order accurate entropy stable adaptive moving mesh finite difference schemes for special relativistic (magneto)hydrodynamics,
  %   submitted to {\em\bfseries J. Comput. Phys.},
  \href{https://arxiv.org/abs/2107.12027}{arXiv: 2107.12027}, Jul 27, 2021.
\end{enumerate}

