\begin{cvsection}{Research Projects}{L{\linewidth-3cm} R{3cm}}
%
\cvprojectentry{2023-2025}{New Efficient Structure-Preserving Numerical Methods for the Multi-dimensional Euler Equations}{design efficient adaptive moving mesh methods and reduced-order models with structure preservation for solving the multi-dimensional Euler equations}{Alexander von Humboldt-Stiftung}{Design and verification of numerical methods. PI}
%
\cvprojectentry{2021-2022}{Sense Dynamics}{construct precise surrogate models of transient nonlinear physical phenomena related to aerodynamics}{Swiss Data Science Center}{Design and verification of numerical simulations for a 3D drone. PI: Dr. Doytchinov Iordan}
%
\cvprojectentry{2021-2022}{High-Order Accurate Adaptive Moving Mesh Methods for Compressible Fluid Flows}{design and verification of high-order accurate adaptive moving mesh methods for solving the Euler and Navier-Stokes equations in 2D and 3D}{National Numerical Windtunnel Project}{Design and verification of numerical methods. PI: Prof. Huazhong Tang}
%
\cvprojectentry{2019-2020}{Computational Methods for the Interface and Elastoplastic Fracture in Fluid Mechanics}{design and verification of high-order accurate adaptive moving mesh methods for solving multi-material flows}{Science Challenge Project}{Design and verification of moving mesh schemes for multi-component flows. PI: Prof. Huazhong Tang}
%
\cvprojectentry{2016-2018}{High-Order Accurate Robust Numerical Schemes for Multi-Material Implosion Hydrodynamics}{research on high-order accurate Lagrangian schemes for solving compressible hydrodynamics}{Science Challenge Project}{Verification of high-order accurate Lagrangian schemes. PI: Prof. Huazhong Tang}
\end{cvsection}
